Introduction to genomics and DNA methylation

### 2015-04-24 Rmarkdown/biology_background.Rmd
Pre-lunch commit. Begin re-write of methsim chapter.

---
title: "Biology background"
output:
  pdf_document:
    fig_caption: yes
    includes:
      in_header: ../latex/header.tex
  html_document:
    keep_md: true
bibliography: ../latex/phd_thesis.bib
---

@@

\begin{chapabstract}
I summarise the basic biology necessary for understanding my thesis. I introduce DNA methylation, describe some of its biological roles, and introduce assays for studying DNA methylation, with a particular focus on bisulfite-sequencing.
\begin{end}

>>>>

---
title: "Introduction to genomics and DNA methylation"
output:
  pdf_document:
    fig_caption: yes
    includes:
      in_header: ../latex/header.tex
  html_document:
    keep_md: true
bibliography: ../latex/phd_thesis.bib
---

@@

\begin{chapabstract}
I summarise the basic biology necessary for understanding my thesis. I introduce DNA methylation, describe some of its biological roles, and introduce assays for studying DNA methylation, with a particular focus on bisulfite-sequencing.
\end{chapabstract}
